`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-20 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
correction to the appendix
more appendix changes
corrected some mistakes in the appendix

\mathcal{F}\left(\phi_i(\mathbf{r})*\psi_j(\mathbf{r}'-\mathbf{r})\right) &=& \left(\pi\sigma_{\phi}^2\sigma_{\psi_j}^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \nonumber \\

@@

 \phi_i(\mathbf{r})*\psi_j(\mathbf{r}'-\mathbf{r}) = \left(\frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} \mathbf r^\top\mathbf r}\right).

@@

 \phi_i(\mathbf{r})*\psi_j(\mathbf{r}'-\mathbf{r}) = \left( \frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2} {\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} (\mathbf r-\boldsymbol\mu_i)^\top(\mathbf r-\boldsymbol\mu_i)}\right).

@@

\section{Inner Product Bit}
The matrix $\Gamma$ is defined as the inner product of the field basis function vector as
\begin{equation}
	\boldsymbol\Gamma = \left[
	\begin{array}{{ccc}} 
		\Gamma_{1,1} & \dots & \Gamma_{1,L} \\
		\vdots & \ddots & \vdots \\
		\Gamma_{L,1} & \dots & \Gamma_{L,L} 
	\end{array}
	\right],
\end{equation}
where
\begin{equation}\label{eq:InofGaussianDefinition}
\Gamma_{1,1} = \phi_i\otimes\phi_j=\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.
\end{equation}
A Gaussian basis function is symmetric with respect to its centre, therefore
\begin{equation}\label{eq:GaussianSymmetry}
 \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r)
\end{equation}
A direct consequence of equation \ref{eq:GaussianSymmetry} is
\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
 \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r)
\end{equation}
substituting equation \ref{eq:ConsequenceofGaussianSymmetry} in equation \ref{eq:InofGaussianDefinition} we have 
\begin{eqnarray}
\phi_i\otimes\phi_j&=&\int_{\mathcal R^n}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&\int_{\mathcal R^n}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i)
\end{eqnarray}
evaluating equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
\begin{equation}
 \phi_i\otimes\phi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
\end{equation}
\section{Notation}

>>>>

\mathcal{F}\left(\phi_i*\psi_j\right)(\mathbf{r}) &=& \left(\pi\sigma_{\phi}^2\sigma_{\psi_j}^2\right)^{\frac{n}{2}}\left(\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \nonumber \\

@@

 \left(\phi_i*\psi_j\right)(\mathbf{r}) = \left(\frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2}{\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} \mathbf r^\top\mathbf r}\right).

@@

 \left(\phi_i*\psi_j\right)(\mathbf{r}) = \left( \frac{\pi\sigma_{\phi}^2\sigma_{\psi_j}^2} {\sigma_{\phi}^2+\sigma_{\psi_j}^2}\right)^{\frac{n}{2}} \mathrm{exp}\left({-\frac{1}{\sigma_{\phi}^2+\sigma_{\psi_j}^2} (\mathbf r-\boldsymbol\mu_i)^\top(\mathbf r-\boldsymbol\mu_i)}\right).

@@

The analytic definition of the observation matrix, $C$, can be derived in a similar fashion, replacing connectivity kernel basis with the sensor.  
\section{Inner Product Bit}
The matrix $\Gamma$ is defined as the inner product of the field basis function vector as
	\boldsymbol\Gamma = \left[
		\Gamma_{1,1} & \dots & \Gamma_{1,L} \\
		\Gamma_{L,1} & \dots & \Gamma_{L,L} 
	\right],
\begin{equation}\label{eq:InofGaussianDefinition}
\Gamma_{i,j} = \phi_i\otimes\phi_j=\int_{\Omega}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf{r}.
A Gaussian basis function is symmetric with respect to its centre, therefore
\begin{equation}\label{eq:GaussianSymmetry}
 \phi_i(\boldsymbol \mu_i+\mathbf r)= \phi_i(\boldsymbol \mu_i-\mathbf r).
Letting $\mathbf{r}= \mathbf{r}-\boldsymbol{\mu}_i$ equation~\ref{eq:GaussianSymmetry} becomes
\begin{equation}\label{eq:ConsequenceofGaussianSymmetry}
 \phi_i(\mathbf r)= \phi_i(2\boldsymbol \mu_i-\mathbf r).
Now substituting equation~\ref{eq:ConsequenceofGaussianSymmetry} into equation~\ref{eq:InofGaussianDefinition} gives 
\phi_i\otimes\phi_j&=&\int_{\Omega}\phi_i(\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&\int_{\Omega}\phi_i(2\boldsymbol \mu_i-\mathbf r)\phi_j(\mathbf r)d\mathbf r\\
&=&(\phi_i*\phi_j)(2\boldsymbol \mu_i).
Evaluating equation \ref{eq:ConvoftwoGaussianNonzeroMean} at $\mathbf r=2\boldsymbol\mu_i $ gives
 \phi_i\otimes\phi_j=\left(\frac{\pi\sigma_i^2\sigma_j^2}{\sigma_i^2+\sigma_j^2}\right)^{\frac{n}{2}}\mathrm{exp}\left({-\frac{1}{\sigma_i^2+\sigma_j^2} (\boldsymbol\mu_i-\boldsymbol\mu_j)^\top(\boldsymbol\mu_i-\boldsymbol\mu_j)}\right).
\section{Notation}
